Cool title here

### 2018-02-13 Frontiers_Manuscript/Villasenor-Derbez.tex
Updated manuscript with results section

To perform the evaluation of these reserves we use thre sources of
information. Ecological data come from the annual ecological monitorings
of reserve and control areas, carried out by members from each community
and personnel from the Mexican CSO ``Comunidad y Biodiversidad''
(\href{www.cobi.org.mx}{COBI}). These monitorings record richness and
abundances of fish and invertebrate species in the reservs and control
sites. For fish census, size structures are also collected to derive
biomass. We define control sites as regions with habitat characteristics
similar to the corresponding reserves, and that presumably had the same
probability of being selected as reserves during the design phase. From
all the reserves in these three communities, we use the ones that have
data for reserve and control sites before and after the implementation
of the reserve (n = 4) , thus providing us with a
Before--After--Control--Impact (\emph{i.e.} BACI) design that allows us
to capture and control for temporal and spatial dynamics
\citep{depalma_2018,ferraro_2006-oW}. BACI designs and causal inference
techniques have proven effective to evaluate marine reserves, as they
allow us to causaly attribute observed changes to the intervention
\citep{moland_2013-VP,Villasenor-Derbez_2018}.

@@

\caption{\label{tab:unnamed-chunk-2}\label{table:indicators}List of indicators used to evaluate the effectiveness of marine reserves, grouped by category.}
\centering
\begin{tabular}[t]{l|l}
\hline
Category & Indicador\\
\hline
Biological & Abundance\\
\hline
 & Richness\\
\hline
 & Shannon's diversity index\\
\hline
 & Biomass\\
\hline
 & Abundance of target species (lobsters)\\
\hline
Socioeconomic & Income from target species\\
\hline
 & Landings from target species\\
\hline
Governance & Type of access to the fishery\\
\hline
 & Perceived degree of illegal fishing\\
\hline
 & Reserve surveilance anf enforcement\\
\hline
 & Type of fishing organization\\
\hline
 & Age of the reserve\\
\hline
\end{tabular}
\end{table}

Biological indicators are analyzed with a difference--in--differences
analysis (Eq \ref{eqn:reg_bio}), which allows us to estimate the effect
that the reserve has on the biological indicators by comparing trends
across time and space (\emph{i.e.} reserve and control sites)
\citep{moland_2013-VP,Villasenor-Derbez_2018}. The analysis is performed
with generalized linear models of the form:

\begin{equation}
I = \alpha_{i} + \gamma_{it} Year_t + \beta Zone_i + \lambda_{it} Year_t\times Zone_i + \sigma_jSpp_j + \Pi_{k}Site_k + \epsilon
\label{eqn:reg_bio}
\end{equation}

Where year--fixed effects are represented by \(\gamma_{it} Year_t\),
\(\beta Zone_i\) captures the difference between reserve (\(Zone = 1\))
and control (\(Zone = 0\)) sites, and the interaction term
\(\lambda_{it} Year_t\times Zone_i\) represents the average treatment
effect for each year. When evaluating biomass and abundances, we include
species--fixed effects (\(\sigma_j\)), and when more than one reserve is
present we also include site--fixed effects (\(\Pi_k\)). For abundances
(\emph{i.e.} count data) the model is estimated with a quasipoisson
error distribution.

@@

A continuación se presentan los resultados de cada una de las
comunidades. Los resultados biológicos se presentarán para cada
comunidad, discutiendo primero los indicadores en común con otras
comunidades (Shannon, Riqueza, Densidad, Nivel Trófico, Biomasa para
peces e invertebrados) y, según su caso, las densidades de las especies
objetivo. Habiendo presentado los resultados biológicos, nos enfocaremos
después en los socioeconómicos y de gobernanza. Usaremos esta
información para identificar las causas (sociales) del éxito (biológico)
de las reservas.

\begin{figure}
\centering
\includegraphics{Villasenor-Derbez_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{\label{fig:unnamed-chunk-3}\label{fig:indicators}Effect sizes for
marine reserves from Isla Natividad (IN; red cirlcles), Maria Elena (ME;
blue triangles), and Punta Herrero (PH; green squares) for
community-levell indicators. Plots are ordered by survey type (left:
fish; right: invertebrates) and indicators: Abundance (A, B), Richness
(C, D), Shannon's diversity index (E, F), and fish biomass (G)}
\end{figure}

\begin{figure}
\centering
\includegraphics{Villasenor-Derbez_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{\label{fig:unnamed-chunk-4}\label{fig:lobsters}Effect sizes for
lobster abundances in marine reserves from Isla Natividad (IN; red
romboids), Maria Elena (ME; blue triangles), and Punta Herrero (PH;
green squares).}
\end{figure}

@@

@@

Maps of the marine reserves and corresponding control sites at each
community.

@@

Table with a general overview of on the governance characteristics of
each community.

>>>>

To perform the evaluation of these reserves we use thre sources of
information. Ecological data come from the annual ecological monitorings
of reserve and control areas, carried out by members from each community
and personnel from the Mexican CSO ``Comunidad y Biodiversidad''
(\href{www.cobi.org.mx}{COBI}). These monitorings record richness and
abundances of fish and invertebrate species in the reservs and control
sites. For fish census, size structures are also collected to derive
biomass. We define control sites as regions with habitat characteristics
similar to the corresponding reserves, and that presumably had the same
probability of being selected as reserves during the design phase. From
all the reserves in these three communities, we use the ones that have
data for reserve and control sites before and after the implementation
of the reserve. This provides us with a Before--After--Control--Impact
(\emph{i.e.} BACI) design that allows us to capture and control for
temporal and spatial dynamics \citep{depalma_2018,ferraro_2006-oW}. BACI
designs and causal inference techniques have proven effective to
evaluate marine reserves, as they allow us to causaly attribute observed
changes to the intervention
\citep{moland_2013-VP,Villasenor-Derbez_2018}. All reserves were
surveyed annualy from at least one year before implementation until
2016. Table \ref{tab:com_sum} shows a summary of the number of reserves,
year of implementation, and number of transects for each reserve.

\begin{table}

\caption{\label{tab:unnamed-chunk-2}\label{tab:com_sum} Summary of commuity--based marine reserves by community. Imp = Year of implementation, Start = Year of first sampling, number of fish transects in control (Cf) and reserve (Rf) sites, and number of invertebrate transects in Control (Ci) and Reserve (Ri) sites.}
\centering
\begin{tabular}[t]{l|l|r|r|r|r|r|r}
\hline
Community & Reserve - Control & Imp & Start & Cf & Rf & Ci & Ri\\
\hline
Isla Natividad & La Plana / Las Cuevas - La Dulce / Babencho & 2006 & 2006 & 405 & 242 & 415 & 245\\
\hline
Maria Elena & Cabezo - Cabezo (Control) & 2012 & 2012 & 44 & 45 & 27 & 21\\
\hline
Punta Herrero & El Faro - El Faro (Control) & 2013 & 2013 & 39 & 40 & 24 & 32\\
\hline
Punta Herrero & Manchon - Manchon (Control) & 2013 & 2012 & 43 & 45 & 27 & 42\\
\hline
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-3}\label{table:indicators}List of indicators used to evaluate the effectiveness of marine reserves, grouped by category.}
\centering
\begin{tabular}[t]{l|l}
\hline
Category & Indicador\\
\hline
Biological & Abundance\\
\hline
 & Richness\\
\hline
 & Shannon's diversity index\\
\hline
 & Biomass\\
\hline
 & Abundance of target species (lobsters)\\
\hline
Socioeconomic & Income from target species\\
\hline
 & Landings from target species\\
\hline
Governance & Type of access to the fishery\\
\hline
 & Perceived degree of illegal fishing\\
\hline
 & Reserve surveilance anf enforcement\\
\hline
 & Type of fishing organization\\
\hline
 & Age of the reserve\\
\hline
\end{tabular}
\end{table}

Biological indicators are analyzed with a difference--in--differences
analysis (Eq \ref{eqn:reg_bio}), which allows us to estimate the effect
that the reserve has on the biological indicators by comparing trends
across time and treatments
\citep{moland_2013-VP,Villasenor-Derbez_2018}. The analysis is performed
with generalized linear models of the form:

\begin{equation}
I_i = \alpha_{i} + \gamma_{it} Year_t + \beta Zone_i + \lambda_{it} Year_t\times Zone_i + \sigma_jSpp_j + \epsilon
\label{eqn:reg_bio}
\end{equation}

Where year--fixed effects are represented by \(\gamma_{it} Year_t\), and
\(\beta Zone_i\) captures the difference between reserve (\(Zone = 1\))
and control (\(Zone = 0\)) sites. The interaction term
\(\lambda_{it} Year_t\times Zone_i\) represents represent the mean
change in the indicator inside the reserve, for year \(t\), with respect
to the first year of evaluation in the control site (See Table
\ref{tab:com_sum}). When evaluating biomass and abundances, we include
species--fixed effects (\(\sigma_j\)). For abundances and richness
(\emph{i.e.} count data) the model is estimated with a quasipoisson
error distribution.

@@

Our methodological approach with biological indicators allows us to make
a causal link between the implementation of marine reserves and the
observed trends by accounting for temporal and spatial dynamics
\citep{depalma_2018}. The effect of the reserve is captured by the
\(\lambda_t\) coefficient, and represents the difference observed
between the control site before the implementation of the reserve and
the reserve site at time \(t\) after controling for other time and space
variations (\emph{i.e.} \(\gamma_t\) and \(\beta\) respectively). Here
we present the effect that marine reserves had on each of the biological
indicators for each coastal community, along with the trends in
socioeconomic indicators of lobster catches and revenues. We also
provide an overview of the state of the socioeconomic and governance
settings of each community, and discuss how these dimensions might be
intertwined with each other.

\subsection{Biological}\label{biological}

Effect sizes for biological indicators are shown in Figure
\ref{fig:indicators}. Isla Natividad, the community with the oldest
reserve, shows inconsistent effects across indicators and sources of
data (\emph{i.e.} fish vs.~invertebrates). For example, the reserve had
a small effect on fish abundances (Fig \ref{fig:indicators}A), where
only year 2010 showed significat effect sizes in fish abundances
(\(p<0.05\)) and all other years oscillated above and under zero
(\(p > 0.05\)). However, in the case of invertebrate abundances (Fig
\ref{fig:indicators}B), there was a clear positive effect of the
reserve, as all but 1 year (2008) presented positive effect sizes
relative to the control site (\(p < 0.05\)). Maria Elena and Punta
Herrero showed no significant increase in fish and invertebrate
abundances (\(p< 0.05\)), except for invertebrates in Punta Herrero for
2014 --right after the implementation of the reserves-- which showed a
significant increase (\emph{i.e.} \(\lambda_{2014} = 2.5\),
\(p < 0.05\)). Full tables with model coefficients are presented in the
supplementary materials (\textbf{S1 Table}, \textbf{S2 Table},
\textbf{S3 Table}).

While the number of fish species oscillated above and bellow zero
through time for all reserves, none of these changes were statistically
significant (\(p > 0.05\)) indicating that the reserves had no effect on
fish species richness (Fig \ref{fig:indicators}C). For invertebrate
species in Isla Natividad, all effect sizes were negative, but only
significant for 2008, 2009, 2011, and 2014 (\(p < 0.05\); Fig
\ref{fig:indicators}D). For Maria Elena and Punta Herrero, the data do
not show significant changes in invertebrate species richness
(\(p > 0.05\)).

Effect sizes for Shannon's diversity index for fish (Fig
\ref{fig:indicators}E) in Isla Natividad oscillated between
\(\lambda_{2011} = -0.45\) and \(\lambda_{2010} = -0.005\), but were not
significantly different from null hypotheses of no change (\emph{i.e.}
\(\lambda_t = 0\); \(p > 0.05\)). For invertebrates in that same
community (Fig \ref{fig:indicators}F), Shannon's diversity index showed
a significant decrease between 2008 and 2014, with largest decrease
observed for 2011 (\(\lambda_{2011} = -0.91\); \(p < 0.05\)). In the
case of Maria Elena and Punta Herrero, Shannon's diversity index for
fish showed increases in the order of \(\lambda_t = 1\). For Maria Elena
and Punta Herrero, these effects were only statistically significant for
2014, and 2014 and 2015 (\(p < 0.05\)).

Biomass was only evaluated for fish data (Fig \ref{fig:indicators}G). In
Isla Natividad, fish biomass presented a steady but small increase
(\(p>0.05\)), and exhibited an increased variability in biomass between
2013 and 2016. Maria Elena and Punta Herrero also showed small,
non-statistically significant increases in fish biomass (\(p>0.05\)).
The last biological indicator is abundance of target species,
\emph{Panulirus interruptus} and \emph{P. argus}, for the Pacific and
Caribbean, respectively (Fig \ref{fig:indicators}H). Isla Natividad
presented small constantly-positive effects but were not significantly
different from the reference point of control site before the
implementation of the reserve (\(p > 0.05\). Maria Elena showed
significant increases in lobster densities in the order of
\(\lambda_t = 10\) (\(p < 0.05\)). Finally, punta herrero presented
alternating negative and positive effects, but these were not different
from the baseline case (\(p > 0.05\)).

\begin{figure}
\centering
\includegraphics{Villasenor-Derbez_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{\label{fig:unnamed-chunk-4}\label{fig:indicators}Effect sizes for
marine reserves from Isla Natividad (IN; red cirlcles), Maria Elena (ME;
blue triangles), and Punta Herrero (PH; green squares) for
community-levell indicators. Plots are ordered by survey type (left:
fish; right: invertebrates) and indicators: Abundance (A, B), Richness
(C, D), Shannon's diversity index (E, F),fish biomass (G), and lobster
(\emph{Panulirus spp}) abundances (H). Points are jittered hotizontally
to avoid overplotting. Points indicate the effect size, and errorbars
are heteroskedastic-robust standard errors.}
\end{figure}

\subsection{Socioeconomic}\label{socioeconomic}

\begin{figure}
\centering
\includegraphics{Villasenor-Derbez_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{\label{fig:unnamed-chunk-5}\label{fig:lobsters}Time series of
lobster catches (A) and revenues (B) in at Isla Natividad (IN; red
circles), Maria Elena (ME; blue triangles), and Punta Herrero (PH; green
squares).}
\end{figure}

\subsection{Governance}\label{governance-1}

@@

The biological effects of the reserve contrast the existing literature.
Why no effect on bio? IN hypoxia. ME and PH, age? Perhaps is the use of
causal inference methods?

Isla natividad no funciona por hipoxya

Maria Elena funciona ``bien''

Punta Herrero no funciona por poaching.

Aun con las mejores caracteristicas sociales, noe s posible vencer al
ambiente (IN). Para el Caribe, parece ser que buena vigilancia y poca
pesca ilegal son determinantes para obtener buenos resultados.
Preguntarle a Stuart si ME solamente se pesca durante lanosta, y todo el
ano es reserva.

IN captures more dynamics. Reflects hypoxia events. Citar paper Giron

Differences between fish and inverts sheds a lights on direct and
indirect effects (Paper que recomendo Fio).

@@

Timeseries of indicators for IN

\paragraph*{S2 Figure}
\label{S2_Figure}

Timeseries of indicators for ME

\paragraph*{S3 Figure}
\label{S3_Figure}

Timeseries of indicators for PH

\paragraph*{S1 Table}
\label{S1_Table}

Coefficient estimates for Isla Natividad

@@

Coefficient estimates for Maria Elena

\paragraph*{S3 Table}
\label{S3_Table}

Coefficient estimates for Punta Herrero
